---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r setup}
library(igraph)
library(frequentgraphs)
library(magrittr)
```


# Example graphs

```{r}
# runif(1)
set.seed(0.8662903)

lattice <- make_lattice(dimvector = c(20,20))
star <- make_star(n = 15)

```

## Example scalar graph statistic

Say we're interested in the mean closeness of largest connected component of the graph:

```{r}
mean_closeness<-function(g,...){
  giant_comp <- g_largest_component(g)
  mean(closeness(giant_comp,...))
  }
```

## Hypothesis test

```{r,warning=FALSE}

# lattice
lattice_test <- g_test_scalar(g = lattice,
                              simulation.n = 300,
                              scalar.graph.statistic = mean_closeness)

lattice_test$observed
lattice_test$simulated.mean
lattice_test$p.value
lattice_test$normality.condition.met

```

The lattice has a much smaller mean closeness than the largest component of same size graphs with a uniformly random edge distribution on average.
The probability that a uniform random distribution of edges produces an average degree centrality as high as the lattice is < `r ceiling(lattice_test$p.value*1000)/1000`.

The test statistic is not normally distributed, so this result should not be taken too serious. 
We should have a look at the distribution:

```{r, fig.width=8,fig.height=6}
g_test_scalar_plot(lattice_test)
```


In comparison, a Barabasi-Albert model graph:
```{r}

g <- igraph::ba.game(100,m = 3)
plot(g)
  g_test_scalar(g,
                simulation.n = 100,
                scalar.graph.statistic = mean_closeness,
                na.rm = TRUE) %>% 
  g_test_scalar_plot

```

In comparison, a  Geometric random graph:
```{r}

g <- igraph::grg.game(100,radius = 0.5)
plot(g)
  g_test_scalar(g,
                simulation.n = 100,
                scalar.graph.statistic = mean_closeness,
                na.rm = TRUE) %>% 
  g_test_scalar_plot


```



